Verifying Demonstrations

### 2018-11-30 paper/adversary-model.tex
removes framing in definitions, edits, adds to auxilliary data explanation

We now provide a concretely defined system and adversary model.
We give three definitions, each defining an adversary with increasingly stronger 
capabilities (\ie more auxiliary information).

@@

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the base adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate.
    They exchange protocol data, \(d_{P,W}(\cid, P)\), and record the time it 
    happened, \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who records the time it happened, \(t_{P,S}\).
    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
    \(A\) (from \cref{in-system-adversary}).
  }
\end{figure}

\begin{adversaries}
\item\label{in-system-adversary}
  \emph{In-system adversary}:
  The adversary maliciously controls \(W\).
  The adversary honest-but-curiously controls \(S\).
  The adversary only learns the protocol data --- \ie what is sent over the 
  channel, no auxiliary data\footnote{%
    By auxiliary data we mean any data outside of the protocol.
    \Eg meta-data such as who is on the other side of the channel.
  }

>>>>

% We now provide a concretely defined system and adversary model.
% We give three definitions, each defining an adversary with increasingly stronger 
% capabilities (\ie more auxiliary information).

@@

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the in-system adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate.
    They exchange protocol data as a function \(d\) of the protest and protester, \(d_{P,W}(\cid, P)\), and record the time it 
    happened, \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who records the time that happened, \(t_{P,S}\).
    Both the witness \(W\) and the storage \(S\) are controlled by the adversary 
    \(A\) (from \cref{in-system-adversary}).
  }
\end{figure}

\begin{adversaries}
\item\label{in-system-adversary}
  \emph{In-system adversary}:
  The adversary maliciously controls \(W\).
  The adversary honest-but-curiously controls \(S\).
  The adversary only learns the protocol data --- \ie what is sent over the 
  channel, no auxiliary data\footnote{%
    By auxiliary data we mean any data outside of the protocol, \ie
    meta-data such as who is on the other side of the channel obtained
    as side information, \eg by face recognition or inference from address
    to identiy.
  }
